full title

### 2020-11-02 paper/pldi21/abstract.tex
Revised intro

\begin{abstract}
  JavaScript becomes one of the most widely used programming languages for web
  development, server-side programming, and embedded systems.  However, its
  dynamic language features degrade the scalability and precision of the static
  analysis.  Moreover, the variety of built-in functions and host environments
  requires excessive manual modeling of their behaviors for the static analysis
  of real-world JavaScript applications.  To alleviate this problem, several
  researchers utilize the dynamic analysis to take its advantage during
  JavaScript static analysis.  However, most of them sacrifice the soundness
  and focus on only reducing the effort of manual modeling.

  In this paper, we propose a novel \textit{dynamic shortcut} technique to
  leverage high performance of dynamic analysis for static analysis in a sound
  way.  It could significantly accelerate the JavaScript static analysis by
  using the highly-optimized commercial JavaScript engines for the concretely
  executable program parts.  Moreover, it might improve the precision and lessen
  the modeling effort by performing dynamic analysis for opaque codes.  To
  maximize the usage of dynamic analysis, we propose \textit{sealed symbolic
  execution}, which is an augmented concrete execution that represents abstract
  values as sealed symbolic values.  We formally define the static analysis with
  dynamic shortcut using sealed symbolic execution.  We actualize our method via
  $\tool$, which is an extension of the existing JavaScript static analyzer
  $\safe$ with dynamic shortcut.  For evaluation of $\tool$, we analyzed
  abstracted versions of \inred{77} official tests of \inred{Lodash 4} library.
  Our tool is \inred{X.X}x faster than the original static analysis on average.
  Moreover, it improves \inred{XX.XX}\% of analysis precision by using dynamic
  analysis instead of static analysis for \inred{XX.X} opaque functions on
  average.
\end{abstract}

>>>>

\begin{abstract}
  JavaScript becomes one of the most widely used programming languages for web
  development, server-side programming, and even micro-controllers for IoT.
  However, its dynamic language features degrade the scalability and precision
  of the static analysis.  Moreover, the variety of built-in functions and host
  environments requires excessive manual modeling of their behaviors.  To
  alleviate this problem, several researchers utilize dynamic analysis to take
  its advantage during JavaScript static analysis.  However, most of them cannot
  fully utilize high performance of dynamic analysis and sacrifice the soundness
  of static analysis.

  In this paper, we propose a novel \textit{dynamic shortcut} technique to
  leverage high performance of dynamic analysis for static analysis by freely
  switching between them in a sound way.  It could significantly accelerate the
  JavaScript static analysis by using the highly-optimized commercial JavaScript
  engines for the concretely executable program parts.  Moreover, it might
  improve the precision and lessen the modeling effort by performing dynamic
  analysis for opaque codes.  To maximize the usage of dynamic analysis, we
  propose \textit{sealed symbolic execution}, which is an augmented concrete
  execution that represents abstract values as sealed symbolic values.  We
  formally define the static analysis with dynamic shortcut using sealed
  symbolic execution.  We actualize our method via $\tool$, which is an
  extension of the existing JavaScript static analyzer SAFE with dynamic
  shortcut.  For evaluation of $\tool$, we analyzed abstracted versions of
  \inred{77} official tests of \inred{Lodash 4} library.  Our tool is
  \inred{X.X}x faster than the original static analysis on average.  Moreover,
  it improves \inred{XX.XX}\% of analysis precision by using dynamic analysis
  instead of static analysis for \inred{XX.X} opaque functions on average.
\end{abstract}

### 2020-11-02 paper/pldi21/eval.tex
Revised intro

\section{Authors and Affiliations}

Each author must be defined separately for accurate metadata
identification. Multiple authors may share one affiliation. Authors'
names should not be abbreviated; use full first names wherever
possible. Include authors' e-mail addresses whenever possible.

Grouping authors' names or e-mail addresses, or providing an ``e-mail
alias,'' as shown below, is not acceptable:
\begin{verbatim}
  \author{Brooke Aster, David Mehldau}
  \email{dave,judy,steve@university.edu}
  \email{firstname.lastname@phillips.org}
\end{verbatim}

The \verb|authornote| and \verb|authornotemark| commands allow a note
to apply to multiple authors --- for example, if the first two authors
of an article contributed equally to the work.

If your author list is lengthy, you must define a shortened version of
the list of authors to be used in the page headers, to prevent
overlapping text. The following command should be placed just after
the last \verb|\author{}| definition:
\begin{verbatim}
  \renewcommand{\shortauthors}{McCartney, et al.}
\end{verbatim}
Omitting this command will force the use of a concatenated list of all
of the authors' names, which may result in overlapping text in the
page headers.

The article template's documentation, available at
\url{https://www.acm.org/publications/proceedings-template}, has a
complete explanation of these commands and tips for their effective
use.

Note that authors' addresses are mandatory for journal articles.

>>>>

\section{Evaluation}\label{sec:eval}

\begin{itemize}
  \item \textbf{RQ1) Analysis Speed-up:} How much analysis time is reduced by
    adding dynamic shortcut to static analysis?
  \item \textbf{RQ2) Precision Improvement:} How much analysis precision is
    improved by replacing the manual modeling with dynamic shortcut?
  \item \textbf{RQ3) Opaque Function Coverage:} How many opaque functions are
    covered by dynamic shortcut without using manual modeling?
\end{itemize}

### 2020-11-02 paper/pldi21/intro.tex
Added img/ directory
Revised intro

\section{Introduction}\label{sec:intro}
JavaScript is the de facto programming language in web development and,
moreover, blossoming beyond the web.
JavaScript has dominated client-side scripting of the web for over a decade.
JavaScript takes the unique position as the universal language operating in both
the browser and on a server in the form of Node.js.
The client-side frameworks such as React, Vue.js, and Angular have accelerated
the universal use of JavaScript.
The cross-platform frameworks like React Native and Electron have spread
JavaScript to the new domains of mobile and desktop beyond the web.
This is only possible thanks to JavaScript's easy operation in development and
deployment with scripting language characteristics such as dynamic and
interpreted language features~\cite{weaklySPE}.

However, such features make it difficult to support developer tools that require
statically reasoning about semantics of JavaScript programs such as call graph
construction, type checking, optimization, and bug detection.
For example, the combination of the JavaScript features: dynamically-computed
property name, prototype chain, and first-class function, makes call graph
construction challenging.
Even a minor precision loss at property name can cause reading all methods in
the object and its prototype chain, including hundreds of built-ins, that
results in useless analysis results.
In static analyses of Java, the benchmark results clearly show the trade-off
between precision and performance~\cite{introspective, data-driven}, a low degree of
context sensitivity shows a high performance but low precision.
In the case of JavaScript, the relationship between precision and performance is
more complex due to the spurious callee explosion.
Low precision tends to cause the large number of spurious callees, which
significantly degrades the performance~\cite{correlation, determinacy-jQuery, weaklySPE, value-refinement}.

For this reason, recent studies on JavaScript static analysis have developed
to improve analysis precision against this challenge.
Madsen et al.~\cite{string, regex, combining-string} presented sophisticated abstract domains for strings.
Park et al. proposed higher degrees of context sensitivity for loops~\cite{lsaECOOP, lsaSPE}.
Relations between object properties have aided to analysis precision~\cite{correlation, weaklyAPLAS, weaklySPE}.
The idea stretches from property name to non-local variables and types for predicate functions~\cite{value-partitioning}.
The on-demand backward analyses~\cite{value-refinement} refines imprecise values for property writes.

Unfortunately, it does not mean that high precision leads to "good" performance
but "better" than the "bad" performance.
Computation costs of high degree of sensitivity remains as it is but the
snowball of low precision is much larger than that.
We alleviate computation costs of high degrees of sensitivity through a combined
approach of static and dynamic analyses.

Existing combined approaches derive three kinds of benefits of dynamic analysis.
Dynamic analyses~\cite{jalangi, dlint} can run on a highly-optimized
JavaScript engine like V8, so it can boost up analysis performance.
There is no precision loss coming from limitations of abstract domains and
sensitivities if the dynamic analysis terminates~\cite{determinacy, concerto}.
Dynamic analysis can pass by opaque codes that require extra handling for static
analysis~\cite{battles, sra}.

However, the existing combined analyses are limited to maximize benefits of
dynamic analysis.
Staged analyses first collect particular information by dynamic analysis and
apply static analysis augmented with dynamic information~\cite{blendedJava, eha}.
Dynamic information can be determinacy facts~\cite{determinacy}, call graphs~\cite{tunable}
object creation site~\cite{blendedJS}, or entire heap at specific program points~\cite{battles}.
Once static analysis starts, it does not utilize more dynamic information.
The other design of combined analysis is divide whole program into two parts~\cite{concerto}.
One (framework code) for the dynamic analysis  and the other (user code) for the
static analysis.
The policy to divde a program is predefined and syntactic and never changes
during analysis.

We present a more flexible and fine-grained method to combine two analyses to
maximize benefits.
Our approach extend dynamic analysis to work with the presence of abstract
values, named lazy concrete execution.
The analysis goes on a concrete engine side as much as possible until
non-determinism is actually introduced by abstract values or analysis
sensitivity that the lazy concrete execution cannot handle.
When the lazy concrete exeuction meets non-determinism, the analysis switches to
the traditional static analysis and uses its abstract semantics to handle that.
As soon as analysis sensitivity is deterministic, it switches to the lazy
concrete execution again.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{benchmark_performance}
  \caption{The performances of static and dynamic analyses on deterministic benchmarks}
  \label{fig:performance}
\end{figure}

Our key observation is that high degrees of sensitivity increase the use of
concrete semantics during analysis and utilizing an optimzied engine like V8 is
the fast way to apply concrete semantics.
As shown in Figure~\ref{fig:performance}.
Our design is not limited to any predefined features including program point and
does not harmful to the soundness of the original static analysis.

%We have demonstrated how dynamic shortcut maximize benefits of dynamic analysis.
%We have implemetned our method by extending the existing JavaScript static
%analyzer.
%We found that using dynamic shortcut significantly increased performance for
%benchmark programs enhanced with abstracted input.

In summary, the contributions of this paper are as follows.
\begin{itemize}
\item We formally describe the high-level idea of adding dynamic shortcuts, a
  technique for combining static and dynamic analyses into fine-grained level on
  the general abstract interpretation framework (Section 3).
  We explain JavaScript related details formalized with core language of JavaScript as well (Section 4).
\item We actualize our method by extending the existing JavaScript static analyzer SAFE 2.0.
  We explain key techniques to synchronize two analyses (Section 5).
\item We empirically evaluate our technique using the implementation (Section 6).
  We find that using dynamic shortcut significantly increased performance for
  benchmark programs enhanced with abstracted input that existing combined
  analysis designs cannot handle.
\end{itemize}

%There are almost 200 million active websites out of over 1.8 billion sites on the entire web.
%https://www.internetlivestats.com/total-number-of-websites/
%JavaScript is used as client-side programming language by 96.9\% of all the websites.
%https://w3techs.com/technologies/history_overview/client_side_language/all/y

>>>>

\section{Introduction}\label{sec:intro}

Over the past decade, the rise of JavaScript as the de facto programming
language in web development has expanded its reach to diverse fields.
Node.js~\cite{nodejs} supports server-side programming, React
Native~\cite{react-native} and Electron~\cite{electron} produce cross-platform
applications.  Moreover, Moddable~\cite{moddable} and Espruino~\cite{espruino}
provide JavaScript environments in micro-controllers for IoT.  Such wide prevalent
usage places JavaScript at \#7 in TIOBE Programming Community
index\footnote{https://www.tiobe.com/tiobe-index/}.  Thus, researchers have
developed static analyzers such as JSAI~\cite{jsai}, TAJS~\cite{tajs},
WALA~\cite{wala}, and SAFE~\cite{safe,safe2} to understand behaviors of
JavaScript programs and to detect their bugs in a sound way.

However, static analysis of real-world JavaScript programs suffers from its
dynamic language features.  JavaScript supports various \textit{dynamic language
features} such as high-order functions, first-class property names, and dynamic
code generations.  While they provide great flexibility in development but it is
challenging to statically analyze such features.  To overcome this problem,
researchers have proposed several analysis techniques: advanced string
domains~\cite{string, regex, combining-string}, loop sensitivity~\cite{lsaECOOP,
lsaSPE}, property relation based analysis~\cite{correlation, weaklyAPLAS,
weaklySPE, value-partitioning}, and on-demand backward
analysis~\cite{value-refinement}.

At the same time, various JavaScript host environments require excessively
manual modeling of their behaviors for static analysis.  Built-in functions and
host-dependent functions are implemented in another native language like C++
instead of JavaScript thus their codes are \textit{opaque} during static
analysis.  Thus, we need to manually model their behaviors but it is
error-prone, tedious, and labor-intensive.  While several automatic modeling
techniques~\cite{safewapi, model-ts} have been proposed, they utilize only type
information thus they generate imprecise modeling compared to the manual
approach.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{img/performance_v8v7}
  \vspace*{-2em}
  \caption{The performances of dynamic analysis and static analysis for V8
  benchmarks (version 7)}
  \label{fig:performance}
  \vspace*{-1em}
\end{figure}

Instead of advancing static analysis techniques, several researchers leverage
dynamic analysis to resolve such obstacles in static analysis.  Dynamic
analyzers such as Jalangi~\cite{jalangi} and DLint~\cite{dlint} run on a
highly-optimized commercial JavaScript engine thus they are much faster than
static analysis.  Figure~\ref{fig:performance} shows that the dynamic analysis
(Jalangi) is \inred{X.X}x faster than static analysis (SAFE) for V8 benchmarks
(version 7).  Using high performance dynamic analysis, several researchers
reduce the scope of static analysis~\cite{determinacy, blendedJS}, construct
initial abstract state~\cite{battles, eha}, and automatic modeling of opaque
codes~\cite{sra}.

Unfortunately, existing techniques using dynamic analysis for static analysis
have two limitations: 1) it cannot fully utilize the high performance of dynamic
analysis, and 2) it sacrifices the soundness of static analysis.  Most of
existing techniques are \textit{staged analyses} that first extract specific
information via dynamic analysis and utilize it in static analysis;
\citet{determinacy} identifies determinate expressions that always have the same
value at given program point, \citet{blendedJS} extract the dynamic values to
change expressions as certain literals, and Park et al.~\cite{battles,eha} dump
initial states in a certain host environment or the entry of an event handler.
However, they cannot utilize dynamic analysis any more after starting static
analysis thus they disturb to maximize the performance advantage.  Moreover,
they sacrifice the soundness of static analysis to perform dynamic analysis.
For example, \citet{sra} utilize dynamic analysis for opaque codes with given
abstract arguments during static analysis.  However, they randomly sample finite
concrete values for given abstract arguments when they represent infinite number
of values.  Thus, the analysis result becomes unsound because of the missing
concrete values.

In this paper, we propose a novel \textit{dynamic shortcut} technique to
leverage high performance of dynamic analysis for static analysis by freely
switching between them in a sound way.  Our key observation is that we can
use concrete semantics for specific program parts while preserving the soundness
if they are not dependent with meaning of abstract values.  For example, the
third line of the following program passes the abstract value \jscode{absval}
stored in \jscode{obj.p1} to the variable \jscode{x}:
\begin{lstlisting}[style=myJSstyle,numbers=none]
var absval = ... // an abstract value
var obj = { p1: absval }, y = "p";
x = obj[y + 1];
\end{lstlisting}
Even though \jscode{obj} contains an abstract value \jscode{absval}, the
semantics of the third line does not dependent with the meaning of
\jscode{absval}.  To utilize this observation in dynamic shortcut, we introduce
\textit{sealed symbolic execution}, which is an augmented concrete execution
with sealed symbolic values.  We represent each abstract value as a sealed
symbolic value, which is a symbolic value that throws an error when trying to
access its actual meaning.  To evaluate our approach, we implemented $\tool$ by
extending the existing JavaScript static analyzer SAFE with dynamic shortcut.
For evaluation of $\tool$, we analyzed abstracted versions of \inred{77}
official tests of \inred{Lodash 4} library.

Our contributions in this paper include the following:
\begin{itemize}
  \item We present a novel \textit{dynamic shortcut} for JavaScript static
    analysis to leverage the high performance of dynamic analysis.  We also
    formally define it with sealed symbolic execution and prove the soundness of
    static analysis using dynamic shortcut.
  \item We actualize dynamic shortcut technique in $\tool$, which is an
    extension of an existing JavaScript static analyzer SAFE with a dynamic
    analyzer Jalangi.
  \item For empirical evaluation, we analyzed \inred{77} official tests of
    \inred{Lodash 4} library with randomly abstracted values.  Our tool
    accelerates \inred{X.X}x the static analysis on average.  Moreover, it
    improves \inred{XX.XX}\% of analysis precision by using dynamic shortcut
    instead of manual modeling for \inred{XX.X} opaque functions on average.
\end{itemize}

In the remainder of this paper, Section~\ref{sec:motivation} explains the
motivation of this work with a simple example.  Section~\ref{sec:formal}
formalizes adding dynamic shortcuts on abstract interpretation.  We extended the
formalization with JavaScript specific language features with a core language in
Section~\ref{sec:javascript}.  Section~\ref{sec:implementation} describes
key techniques to implement dynamic shortcuts for JavaScript static analysis.
We describes evaluation result of our techniques with real-world benchmarks in
Section~\ref{sec:eval}.  Section~\ref{sec:related} explains related works and
Section~\ref{sec:conclusion} concludes.
